%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Samsung Research Institute - Bangalore} % Organization
    {Bangalore, India} % Location
    {Jun. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed various scripts, toolkits and pipelines used by the team for automating and simplifying tasks}
        \item {Worked on language modeling for SVoice and Bixby for the English Language}
        \item {Implemented new features and improved the accuracy of Bixby for English language}
        \item {Developed, released and steadily improved accuracy for Indian Accented English}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Trainee (Intern)} % Job title
    {Samsung Research Institute - Bangalore} % Organization
    {Bangalore, India} % Location
    {May. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an intuitive and efficient interface to :}
       	\subitem{Assist the user in tuning the Automatic Speech Recognition Engine to their domain}
        \subitem{Generate a grammar that can be parsed by the ASR Engine}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {eCourierz} % Organization
    {Chennai, India} % Location
    {Apr. 2014 to Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of a startup, serving as an online marketplace for the courier industry, allowing people to make convenient and informed choices for sending couriers and helps courier companies to effectively connect to this client base.}
        \item {Designed and developed the complete website(backend, frontend and database) for ‘eCourierz’}
        \item {Mentored new joinees regarding the technologies and flow of the site}
        \item {The project is developed using Bootstrap and Less for the UI, and MongoDB, PJAX (pushState + AJAX), Pyramid (a web framework for Python programming language) for the backend.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {VASCOM Tech Ltd.} % Organization
    {Chennai, India} % Location
    {Nov. 2013 to Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned and applied JSP scripting language for designing web pages using struts, beans, DAOs etc.}
      \end{cvitems}
    }


\end{cventries}
